---
Author: "Helen_Liu"
Date: "28/2/2023"
output: html_notebook
---

```{r}
library(tidyverse)
```

#import and preprocess survey data

```{r}
df <- read.csv("health_survey.csv") %>%
  dplyr::select(
    ID = "编号",
    Gender = starts_with("X1"),
    #1 = male, 2 = female
    Age = starts_with("X2"),
    Edu = starts_with("X3"),
    Hour_work = starts_with("X4"),
    SES = starts_with("X5"),
    Diet =  contains("饮食习惯"),
    Exercise = contains("体育锻炼"),
    Sleep = contains("睡眠习惯"),
    Pressure = contains("压力管理"),
    Alcohol = contains("饮酒"),
    Smoke = contains("吸烟"),
    Time = contains("时间不够"),
    Motivation = contains("没有动力或意志力"),
    Money = contains("成本或经济约束"),
    Support = contains("缺乏社会支持"),
    Knowlege = contains("知识或资源"),
    Norm = contains("文化或社会规范")
  ) %>%
  mutate_at("Age", str_replace, "年", "") %>%
  mutate_at("Age", as.numeric) %>%
  mutate(age =
           2023 - Age) %>%
  dplyr::select(-Age) %>%
  mutate(Gender = recode(Gender, "1" = "Male", "2" = "Female")) %>%
  mutate_at(vars("ID", "Gender"), as.factor) %>%
  mutate_at(vars("age", "Hour_work"), as.numeric) 
```

#plot health behaviors 

```{r}
df_plot <- df %>%
  group_by(Gender) %>%
  summarise(
    p_Diet = sum(Diet, na.rm = TRUE) / n(),
    p_Exercise = sum(Exercise, na.rm = TRUE) / n(),
    p_Sleep = sum(Sleep, na.rm = TRUE) / n(),
    p_Pressure = sum(Pressure, na.rm = TRUE) / n(),
    p_Alcohol = sum(Alcohol, na.rm = TRUE) / n(),
    p_Smoke = sum(Smoke, na.rm = TRUE) / n()
  ) %>%
  pivot_longer(cols = p_Diet:p_Smoke,
               names_to = "behaviors",
               values_to = "p_report")  %>%
  mutate_at("behaviors", str_replace, "p_", "") %>%
  mutate_at("behaviors", as.factor)

df_plot$behaviors <- factor(
  df_plot$behaviors,
  levels = c("Diet", "Exercise", "Sleep", "Pressure", "Alcohol", "Smoke")
)


ggplot(df_plot,
       aes(x = behaviors, y = p_report, fill = behaviors)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ Gender) +
  # scale_y_continuous(
  #   limits = c(0, 1))+
  # # Accuracy of y-axis
  scale_y_continuous(limits = c(0, 1),
                     labels = scales::percent_format(accuracy = 1)) + #transfer y to percentage
  geom_text(aes(label = scales::percent(round(p_report, 2))),
            size = 3,
            vjust = -1) +
  theme_bw() +
  labs(x = "Health Behavior", y = "Percentage of Respondent") +
  scale_fill_brewer(palette = "Spectral") +
  theme(
    panel.border = element_blank(),
    #remove border
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    legend.position = "none",
    axis.text.y =  element_text(size = 10,
                                angle = 0),
    axis.text.x =  element_text(
      size = 10,
      angle = 40,
      hjust = 1
    ),
    axis.line = element_line(size = 0.25)
  )
```

#plot barriers 

```{r}
df_plot2 <- df %>%
  group_by(Gender) %>%
  summarise(
    p_Time = sum(Time, na.rm = TRUE) / n(),
    p_Motivation = sum(Motivation, na.rm = TRUE) / n(),
    p_Money = sum(Money, na.rm = TRUE) / n(),
    p_Support = sum(Support, na.rm = TRUE) / n(),
    p_Knowlege = sum(Knowlege, na.rm = TRUE) / n(),
    p_Norm = sum(Norm, na.rm = TRUE) / n()
  ) %>%
  pivot_longer(cols = p_Time:p_Norm,
               names_to = "barriers",
               values_to = "p_report")  %>%
  mutate_at("barriers", str_replace, "p_", "") %>%
  mutate_at("barriers", as.factor)


df_plot2$barriers <- factor(
  df_plot2$barriers,
  levels = c("Time", "Motivation", "Money", "Support", "Knowlege", "Norm")
)

ggplot(df_plot2,
       aes(x = barriers, y = p_report, fill = barriers)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ Gender) +
  # scale_y_continuous(
  #   limits = c(0, 1))+
  # # Accuracy of y-axis
  scale_y_continuous(limits = c(0, 1),
                     labels = scales::percent_format(accuracy = 1)) + #transfer y to percentage
  geom_text(aes(label = scales::percent(round(p_report, 2))),
            size = 3,
            vjust = -1) +
  theme_bw() +
  labs(x = "Perceived Barriers", y = "Percentage of Respondent") +
  scale_fill_brewer(palette = "Spectral") +
  theme(
    panel.border = element_blank(),
    #remove border
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    legend.position = "none",
    axis.text.y =  element_text(size = 10,
                                angle = 0),
    axis.text.x =  element_text(
      size = 10,
      angle = 40,
      hjust = 1
    ),
    axis.line = element_line(size = 0.25)
  )
```

#correlational analysis

```{r}
#preprocess data
df2 <- df %>%
  drop_na(Hour_work) %>%
  filter(SES >= 1 && SES <= 10) %>%
  replace(., is.na(.), 0) %>% ##change all NA into 0
  mutate(n_behavior = Diet +Exercise+Sleep + Pressure +Alcohol+Smoke,
         n_barrier = Time + Motivation + Money + Support +Knowlege + Norm)
```

# Descriptive

```{r}
length(unique(df$ID))  #73 participants 
#
df %>%
  group_by(Gender) %>%
  summarise(n = n ())  #male 23, female 50
#
mean(df$age) #25.90
sd(df$age) #5.64
#
mean(df2$Edu) #4.52
sd(df2$Edu) #0.56
#
mean(df2$Hour_work) #7.45
sd(df2$Hour_work) #2.77
#
mean(df2$SES) #5.38
sd(df2$SES) #1.68

```



```{r}
df_behavior <- df2 %>%
  dplyr::select("Edu":"SES","age","n_behavior","n_barrier") 


#correlation
library(rstatix)
library(corrplot)

  df_behavior %>%
  cor_mat() %>%
  cor_mark_significant() 



colnames(df_behavior) <- c("Education", "Working hours", "SES", "Age","N(Health Behaviors)","N(Barriers)")

mydata.cor <- cor(df_behavior)
testRes = cor.mtest(df_behavior, conf.level = 0.95)
corrplot(
  mydata.cor,
  p.mat = testRes$p,
  method = 'color',
  diag = FALSE,
  type = 'upper',
  sig.level = c(0.001, 0.01, 0.05),
  pch.cex = 0.9,
  insig = 'label_sig',
  pch.col = 'grey20',
  order = 'AOE',
  tl.col = "black" ) #TEXT COLOR
```

#Binary Logistic Regression

Use binary logistic regression to understand how changes in the independent variables are associated with changes in the probability of an event occurring. This type of model requires a binary dependent variable. A binary variable has only two possible values, such as pass and fail.

```{r}
library(MASS)
library(report)

df3 <- df2 %>% dplyr::select(age,Edu,Hour_work,SES,Time) %>% 
  mutate_at("Time",as.factor)
  
logit_1 <- glm(Time ~., 
               family = binomial,
               data = df3)

#Analysis of Model Summary
summary(logit_1)
# stepwise model selection method
logit_1_2 <- stepAIC(logit_1)

#best model:Time ~ Hour_work
logit_hourwork <- glm(Time ~ Hour_work, 
               family = binomial,
               data = df3)

#Analysis of Model Summary
summary(logit_hourwork)
report(logit_hourwork)
#
df4 <- df2 %>% dplyr::select(age,Edu,Hour_work,SES,Motivation) %>% 
  mutate_at("Motivation",as.factor)

logit_2 <- glm(Motivation ~., 
               family = binomial,
               data = df4)
summary(logit_2)

logit_2_2 <- stepAIC(logit_2)

logit_motivation <-  glm(Motivation ~ age + Hour_work, 
               family = binomial,
               data = df4)
summary(logit_motivation)
report(logit_motivation)

```

